The shape of dark matter halos in the AURIGA simulations

### 2019-02-19 Paper/paper.tex
edit

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center give rise to perturbed axial ratios measurments. 
Figure \ref{fig:triax_HDM} shows the same information, this time for
the MHD simulations. 
The main radial trend continues to hold, albeit less pronounced; halos
in MHD simulations are in general rounder than their DM counterparts
and the increased roundness in outer regions is less pronounced on
average.
This average behaviour is more clear in the individual case of Halo 16
in Figure \ref{fig:triaxial_ratios}. There, as we mentioned, at the virial radius the halo is
rounder than its DM counterpart. 
Going from $50$\kpch to
$10$ \kpch radii the $b/a$ ratio is constant almost close to unity
while it decreases to $0.5$ in DM-only simulation

the DM halo is almost perfectly
oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these results for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; b) the comparison
against Table \ref{table:median_axial_ratio_MHD} shows  how DM halos
are consistently rounder in MHD simulations than DM-only runs at every radius.

>>>>

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center gives rise to perturbed axial ratio measurements. 
Figure \ref{fig:triax_MHD} shows the same information, this time for
the MHD simulations. 
In this case, the main radial trend continues to hold, albeit less
pronounced.
We also find that halos in MHD simulations are in general rounder than
their DM counterparts

This average behaviour of more round halos in MHD can be seen more
clearly in the individual case of Halo 16, shown in Figure
\ref{fig:triaxial_radius}.  
At the virial radius the halo is rounder than its DM counterpart. 
Going from the virial radius to $10$ \kpch the $b/a$ ratio is constant almost close to unity
in the MHD simulation while it decreases to $0.5$ in DM-only
simulation. 
Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
the range $0.9-1.0$, while the MHD simulation has values between
$0-0.5$.

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these trends for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; b) the comparison
against Table \ref{table:median_axial_ratio_MHD} shows  how DM halos
are consistently rounder in MHD simulations than DM-only runs at every radius.
